Titeln på avhandlingens språk

### 2023-01-15 body/part1/overview/extending-wca.tex
exectime model

\subsubsection{Designing a realistic model for human timings in \gls{WCA}}

@@

    \item The resulting weighted rolling \gls{TTF} is used to look-up potential values for the execution time in the original data from \cref{paper:olguinmunoz2021impact}.
    We do this by pre-processing the original data from the \num{40} independent repetitions of the LEGO task with this same rolling weighted average formula, and then binning samples according to the resulting \num{7}-quantiles for weighted \glspl{TTF}.
    The weighted \gls{TTF} calculated during runtime is then matched to the corresponding bin of samples.

@@

>>>>

\subsubsection{Design of a realistic model for human timings in \gls{WCA}}

\todo[inline]{Do we need a discussion on why an improved model is necessary?}

@@

    \item The resulting weighted rolling \gls{TTF} is used to look up potential values for the execution time in the original data from \cref{paper:olguinmunoz2021impact}.
    We do this by pre-processing the original data from the \num{40} independent repetitions of the LEGO task with this same rolling weighted average formula, and then binning samples according to the resulting \num{7}-quantiles for weighted \glspl{TTF}.
    The weighted \gls{TTF} calculated during runtime is then matched to the corresponding bin of samples.

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=\textwidth]{Figs/2023EdgeDroid2/model_exectime_over_steps}
    \caption{
        Illustration of the execution times output by the model at fixed values of \glspl{TTF}, over a series of steps, parameterized by levels of neuroticism.
        Shaded bands indicate \SI{95}{\percent} \glspl{CI}.
    }\label{fig:model:exectimesoversteps}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[height=13em]{Figs/2023EdgeDroid2/model_exectimes_transition}
    \caption{%
        Mean execution times generated by the model after a single step at a \gls{TTF} of \SI{2.5}{\second} preceded by a sequence of \num{25} steps at fixed lower (instantaneous feedback) or higher (\SI{5}{\second}) \gls{TTF}.
        Errorbars indicate \SI{95}{\percent} \glspl{CI}.
    }\label{fig:model:exectimestransitions}
\end{figure}

\Cref{fig:model:exectimesoversteps,fig:model:exectimestransitions} illustrate the adherence of the model to the conclusions obtained from our work in \cref{paper:olguinmunoz2021impact}.

\Cref{fig:model:exectimesoversteps} shows the output of the execution time model described above over a series of steps at three levels of \gls{TTF};
\emph{low} (instantaneous feedback), \emph{medium} (\SI{2.5}{\second}), and \emph{high} (\SI{5}{\second}).
When the system is highly responsive (low \glspl{TTF}), the model tends to speed up as the task progresses.
Conversely, at high levels of impairment, execution times depend on strongly on the parameterized level of neuroticism;
as concluded from our previous discussion, higher neuroticism leads to a stronger reaction to reduced responsiveness and subsequently to longer execution times.

In \cref{fig:model:exectimestransitions}, moreover, we present the lingering effects of reduced system responsiveness on \glspl{TTF} generated after the system returns to a more responsive state.
These results were generated by first feeding a sequence of \num{25} identical \glspl{TTF} to the model, with values of either \SI{0}{\second} (i.e.\ instantaneous feedback) or \SI{5}{\second}.
Next, a single \gls{TTF} of \SI{2.5}{\second} was fed to the model, and the generated execution time was recorded.
This procedure was repeated \num{600} times.
As expected from our discussion in \cref{impact:results}, transitions from a higher (\SI{5}{\second}) \gls{TTF} resulted in noticeably inflated execution times (\ensuremath{+\SI{8.5}{\percent}} at a high level of neuroticism) for the first step at \SI{2.5}{\second} \gls{TTF} compared to when the transition was from a lower \gls{TTF}.
